Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-08-29 papers/contact/paper.tex
a few edits to results and discussion of contact paper Tested everything on darcy.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-10}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:inner-4-10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-12-10}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:inner-12-10}
\end{figure}

@@

The $g_\sigma^A$ correlation function in each configuration is very
flat, with only small, smooth changes as the surface is approached.
Our functional $g_\sigma^A$ very closely matches the Monte Carlo
predictions in each case, while that of Gross consistently
underestimates the correlation at the interface by about
\textcolor{red}{few percent}.

The $g_\sigma^S$ correlation function shows considerably more
structure, as well as additional variation due to the curvature of the
hard surface.

@@

We can see that the White Bear DFT calulations for the densities at
varying distances from the respective surfaces match up well with the
monte-carlo simulated densities.  The densities slope up towards and
reach a maximum at the surfaces as the diffusion cutoff in that
direction causes hard spheres to collect. We also see that $n_0$
slopes sharply downward towards the different surfaces, beginning the
trend at about one radius away.  Part of the average that is taken for
spheres in these locations will be taken within a volume for which the
sphere density is uniformily zero. A similar trend is followed by
$n_A$ beginning at about two radii away.  A sphere that is in contact
with another at any position must be two radii away from the center of
the first.  Thus, within two radii of the surface, one enters into a
region where some of the contact volume is past the zero density
boundary.

The $S$ case correlation functions do not match the monte carlo
simulated correlation as well as the functionals of Yu and Wu.  For
the walls and the sperical cavity, the monte carlo simulations show
this function going to zero at these surfaces, roughly beginning its
downward trend at about one sphere radius out.  This stands to reason
since that because there is an increased density up against the wall,
there is little chance that points within a radius of the wall and the
center of those spheres will be a contact point between two spheres,
since the hard spheres cannot overlap.

The $A$ correlation White Bear calculations match up very well with
monte-carlo simulation.  Although they seem to be both very close, the
Gross functional deos not have the near perfect overlap with
simulation that the White Bear calculation deos.

>>>>

@@

The $g_\sigma^A$ correlation function in each configuration is very
flat, with only small, smooth changes as the surface is approached.
Our functional $g_\sigma^A$ very closely matches the Monte Carlo
predictions in each case, while that of Gross consistently
underestimates the correlation at the interface by
\textcolor{red}{several percent}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-10}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:inner-4-10}
\end{figure}

The $g_\sigma^S$ correlation function shows considerably more
structure, as well as additional variation due to the curvature of the
hard surface.  The symmetric correlation function is nonzero at
locations where spheres may touch, which for a convex hard surface
means that $g_\sigma^S$ may be nonzero in the volume in which hard
spheres are excluded.  In every configuration studied, the agreement
between the theoretical predictions and the Monte Carlo simulation in
each case is very poor in the region where there should be no contacts
at all.  Because $n_0$ is comparable to its bulk value in this region,
this means that these functionals predict a significant number of
contacts in the region where there should be none.  The correlation
function of Yu and Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}
and ours described in Section~\ref{sec:g-S} give similar results, with
slightly larger errors in our prediction.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-12-10}
  \caption{Density and contact densities at a xxx with bulk filling
    fraction of 0.1.}
  \label{fig:inner-12-10}
\end{figure}

@@
